### 2022-03-18 sections/systematic_uncertainties.tex
update Luca's comments

Several sources of systematic uncertainty that can affect the normalisation of signal 
and background and/or the shape of their corresponding discriminant distributions are considered.
Each source is considered to be uncorrelated with the other sources.  
Correlations of a given systematic uncertainty are maintained across processes and channels 
as appropriate. The following sections describe the systematic uncertainties considered.
Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematics uncertainties on the measured $\BR(H\to qH)$ branching ratio
resulting from the fits to the data in the signal regions as described in Section~\ref{sec:result}.

@@

Efficiencies to tag $b$-jets and $c$-jets in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aad:2019epj79}, %EPJ C79(2019)970 {Aaboud:2018xwy},
  while the $c$-jet efficiency is measured
using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. 
The light-jet efficiency is measured in a multi-jet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
The uncertainties in these scale factors include a total of 44 independent sources affecting $b$-jets, 19 source affecting $c$-jets, and 19 sources affecting light-jets. 
These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets.

%The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing. However, this uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to data. An uncertainty on these reweighting scale factors is considered based on the disagreement between the instantaneous luminosity in data and in simulation.

@@

Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated to be approximately 30\% by taking the maximum
difference between the data and total background prediction in the different analysis regions considered, but requiring exactly zero, one, and two $b$-jets.
This is mainly limited by the LO MC simulation in the $V$+jets high multiplicity regions.  
%Agreement between data and predicted background 
%in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
%be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
%Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
%of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
%subprocesses, considered uncorrelated between them.

>>>>

Several sources of systematic uncertainty that can affect the normalisation of signal 
and background and/or the shape of their corresponding discriminant distributions are considered.
Each source is considered to be uncorrelated with the other sources.  
Correlations of a given systematic uncertainty are maintained across processes and channels 
as appropriate. The following sections describe the systematic uncertainties considered.
Table~\ref{tab:had_sys_impact} shows a summary of the dominant systematics uncertainties on the measured $\BR(t\to qH)$ branching ratio
resulting from the fits to the data in the signal regions as described in Section~\ref{sec:result}.

@@

Efficiencies to tag $b$-jets and $c$-jets in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aad:2019epj79}, %EPJ C79(2019)970 {Aaboud:2018xwy},
  while the $c$-jet efficiency is measured
using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. 
The light-jet efficiency is measured in a multi-jet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
The uncertainties in these scale factors include a total of 44 independent sources affecting $b$-jets, 19 source affecting $c$-jets, and 19 sources affecting light-jets. 
These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets.
%The uncertainty on the pileup reweighing is evaluated by varying the pileup scale factors by 1$\sigma$ based on the reweighing of the average interactions per bunch crossing. However, this uncertainty is highly correlated with the luminosity uncertainty and may be an overestimate.
Scale factors are applied to reweight simulated events in order to obtain the pile-up distribution corresponding to data.
An uncertainty on these reweighting scale factors is estimated by varying the reweighting to the profile in data within its uncertainties.
%considered based on the disagreement between the instantaneous luminosity in data and in simulation.

@@

Uncertainties affecting the normalisation of the $V$+jets background are estimated separately for $V$+light-jets, $V$+$\geq$1$c$+jets,
and $V$+$\geq$1$b$+jets subprocesses. The total normalisation uncertainty of $V$+jets processes is estimated to be approximately 30\% by taking the maximum
difference between the data and total background prediction in the different analysis regions considered, but requiring exactly zero, one, and two $b$-jets.
This is mainly driven by the disagreement between MC simulation in the $V$+jets regions with high multiplicity of jets.  
%Agreement between data and predicted background 
%in these modified regions, which are dominated by $V$+light-jets, is found to be within approximately 30\%. This bound is taken to 
%be the normalisation uncertainty, correlated across all $V$+jets subprocesses. 
%Since {\sherpa}~2.2 has been found to underestimate $V$+heavy-flavour production by about a factor
%of 1.3~\cite{Aaboud:2017xsd}, additional 30\% normalisation uncertainties are assumed for $V$+$\geq$1$c$+jets and $V$+$\geq$1$b$+jets
%subprocesses, considered uncorrelated between them.
